---
title: "Lab5Doc"
author: "James Boyle"
date: "07/06/2021"
output: github_document
always_allow_html: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, warning = FALSE)
```

```{r, eval = TRUE}
library(ggplot2)
library(dplyr)
library(moderndive)
library(gapminder)
library(skimr)
library(kableExtra)
library(gridExtra)
```


## Introduction {#sec:intro}

This is a test using GitHub. I will also use it to make a report using some data. I will use the evals data to create some stuff.


## Exploratory data analysis {#sec:eda}

First of all, here is a pointless link to the introduction, just to show I can do it \ref{sec:intro}  

Not worked for some reason. Anyway. This report will look for a relationship between beauty score and ethnicity using the evals data.  
It is not written in a professional manner. It's just practice.

```{r data}
evals.bea.eth <- evals %>%
  select(bty_avg, ethnicity)


```

First of all, some summary statistics.

```{r sum}
evals.bea.eth %>%
  group_by(ethnicity) %>%
  summarise(n=n(),  MeanHeart=round(mean(bty_avg),2), SDHeart=round(sd(bty_avg),2), FQ=quantile(bty_avg, 0.25),
            TQ=quantile(bty_avg, 0.75),
            min = min(bty_avg), max=max(bty_avg),
            median=median(bty_avg)) %>%
  kable(col.names = c("Ethnicity","Number", "Beauty score", "SD", "1st Q", "3rd Q", "Min.", "Max","Median"),        
        caption = '\\label{tab:summary} Summary statistics on beauty score by ethnicity.') %>%
  kable_styling(font_size = 10, latex_options = "hold_position")

```

This does not really show much interesting.


Now look at some boxplots



```{r, eval = TRUE, out.width = '80%', fig.align = "center", fig.cap = "\\label{fig:scat} Beauty for ethnicity.", fig.pos = "H"}
ggplot(data = evals.bea.eth, mapping = aes(x = factor(ethnicity), 
                                     y = bty_avg)) + geom_boxplot(fill = "steelblue") + 
  labs(x = "Ethnicity", y = "Beauty score", title = "Beauty score and ethnicity")  + scale_x_discrete(labels = c("minority", "not minority"))
```


